Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-06 paper/figures.tex
Render Alexa rank vs Disconnect organizations figure

>>>>

\tikzsetnextfilename{mini-1x1-alexa-rank-plot}
\begin{tikzpicture}
\begin{semilogxaxis}[
	xlabel=Alexa rank,
	ylabel=Organizations,
	xmin=0,
	xmax=1000000,
	ymin=0,
	xmajorgrids=true,
	ymajorgrids=true,
	% xtick={0,10000,100000,1000000},
	xminorgrids=true,
	enlarge x limits=false,
	enlarge y limits=false,
	height=.25\textwidth,
	width=\textwidth,
	legend columns=1,
	legend style={at={(1.05,0.5)},anchor=west,cells={anchor=west},},
	xticklabel style={
		/pgf/number format/.cd,
		/pgf/number format/fixed,
		/pgf/number format/fixed zerofill=false,
		/pgf/number format/precision=2
	},
	yticklabel style={
		/pgf/number format/fixed,
		/pgf/number format/fixed zerofill=false,
		/pgf/number format/precision=2
	},
]
	% \addplot[
	% 	% only marks,
	% 	blue,
	% 	% opacity=0.2,
	% 	% mark size=0.5pt,
	% ]
	% table[
	% 	x=Rank,
	% 	y=Value,
	% ]
	% \tableAlexaRankBucketsSortedSeRandomHttpWww;

	% \addlegendentry{se.2014-07-10.random.100000-http-www}

	\addplot[
		% only marks,
		orange,
		% opacity=0.2,
		% mark size=0.5pt,
	]
	table[
		x=Rank,
		y=Value,
	]
	\tableAlexaRankBucketsSortedAlexaRandomHttpWww;

	\addlegendentry{alexa.2014-09-01.random.10000-http-www}

	\addplot[
		% only marks,
		green,
		% opacity=0.2,
		% mark size=0.5pt,
	]
	table[
		x=Rank,
		y=Value,
	]
	\tableAlexaRankBucketsSortedAlexaTopHttpWww;

	\addlegendentry{alexa.2014-09-01.top.10000-http-www}

	\addplot[
		% only marks,
		red,
		% opacity=0.2,
		% mark size=0.5pt,
	]
	table[
		x=Rank,
		y=Value,
	]
	\tableAlexaRankBucketsSortedAlexaTopSeHttpWww;

	\addlegendentry{alexa.2014-09-01.top.se.10000-http-www}

	\addplot[
		% only marks,
		purple,
		% opacity=0.2,
		% mark size=0.5pt,
	]
	table[
		x=Rank,
		y=Value,
	]
	\tableAlexaRankBucketsSortedAlexaTopDkHttpWww;

	\addlegendentry{alexa.2014-09-01.top.dk.10000-http-www}
\end{semilogxaxis}
\end{tikzpicture}

### 2015-05-06 paper/tableread.tex
Render Alexa rank vs Disconnect organizations figure

>>>>

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{alexa-rank.buckets.sorted.se.2014-07-10.random.100000-http-www.tsv}\tableAlexaRankBucketsSortedSeRandomHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{alexa-rank.buckets.sorted.alexa.2014-09-01.random.10000-http-www.tsv}\tableAlexaRankBucketsSortedAlexaRandomHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{alexa-rank.buckets.sorted.alexa.2014-09-01.top.10000-http-www.tsv}\tableAlexaRankBucketsSortedAlexaTopHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{alexa-rank.buckets.sorted.alexa.2014-09-01.top.se.10000-http-www.tsv}\tableAlexaRankBucketsSortedAlexaTopSeHttpWww

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{alexa-rank.buckets.sorted.alexa.2014-09-01.top.dk.10000-http-www.tsv}\tableAlexaRankBucketsSortedAlexaTopDkHttpWww
